Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation

### 2011-02-23 Multiresolution_framework/ltx/manuscript.tex
changed the histogram plot

One second of data was generated using equations \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} in response to an initial condition where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $ \eta(r-r')=1.5\times\phi_{4,3,-2}(r-r')$. Sampling time and the synaptic time constant are set to 1 and 10 milliseconds respectively. The sensors were arranged regularly where the distance between adjacent sensors was set to 0.5 mm resulting into 161 observation locations. Sensors are modelled using $\phi_{4,4,k}$, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel. The connectivity kernel and its decomposition are plotted in  \figurename{\ref{fig:KernelAndFreqResponse}} (a). The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b). The observed field has an approximate spatial bandwidth $1.38$ cycles/mm. This suggests the use of wavelets upto level $j=3$.

>>>>

One second of data was generated using equations \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} in response to an initial condition where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $ \eta(r-r')=1\times\phi_{4,3,-2}(r-r')$. Sampling time and the synaptic time constant are set to 1 and 10 milliseconds respectively. The sensors were arranged regularly where the distance between adjacent sensors was set to 0.5 mm resulting into 161 observation locations. Sensors are modelled using $\phi_{4,4,k}$, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel. The connectivity kernel and its decomposition are plotted in  \figurename{\ref{fig:KernelAndFreqResponse}} (a). The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b). The observed field has an approximate spatial bandwidth $1.38$ cycles/mm. This suggests the use of wavelets upto level $j=3$.
